Code Overflow: \\ An empirical study of online code reuse

### 2016-09-23 latex/stackoverflow.tex
Updated Sankey chart

\section*{Raw statistics}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
\subsubsection{Qualitas Original (v. 2013-09-01r)}
\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}. We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 664 \textit{ok-match} pairs that were investigated. The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.

@@

@@

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
		\hline
		Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
		\hline
		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
		\hline
	\end{tabular} 
\end{table}

\subsubsection{Qualitas New (v. 2016-08-05)}
We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

\begin{table}[H]
	\centering
	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
	\label{tab:classification_new}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & A' & B & C & D & E & F & Total \\ 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
		\hline
		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
		\hline
		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification_new}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
		\hline
		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
		\hline
	\end{tabular} 
\end{table}

\subsection{Investigation of the unique clone pairs}
\subsubsection{Qualitas Original (v. 2013-09-01r)}
In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.

@@

\begin{table}[H]
	\centering
	\caption{Classification results of 202 Simian$_{df}$ and 222 NiCad$_{df}$ individual unique pairs.}
	\label{tab:classification_indv}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & A' & B & C & D & E & F & Total \\ 
		\hline 
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 202 \\ \cline{2-8}
		\hline
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 222 \\ \cline{2-8}
		\hline
		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & \multirow{3}{*}{424} \\ 
		& \multicolumn{4}{l|}{\textit{44 unique SO fragments}} & \multicolumn{3}{l|}{380 unique SO fragments} & \\
		& \multicolumn{4}{l|}{\textit{44 unique Q files}} & \multicolumn{3}{l|}{380 unique Q files} & \\
		\hline
	\end{tabular} 
\end{table}

\subsubsection{Qualitas New (v. 2016-08-05)}

\begin{table}[H]
	\centering
	\caption{Distributions of true positive pairs from the investigation of Qualitas (2013-09-01r)}
	\label{tab:tp_pairs}
	\begin{tabular}{l|r|r|r|r|p{5cm}}
	\hline
	Project		& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
	\hline
	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
	%\hline
	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
	Compiere	& 127	& 2		& 178	& 8 & No update \\
	axion		& 7		& 	0	& 12	& 0 & No update \\
	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
	colt		& 0		& 	0	& 5		& 0 & No update \\
	columba		& 14	&	0	& 177	& 0 & No update \\
	drawswf		& 0		&	0	& 0		& 0 & No update \\
	fit-java	& 0		& 0		& 2 	& 0 & No update \\
	freecs		& 5		& 0		& 22	& 0 & No update \\
	heritrix	& 16	& 0		& 190 	& 0 & No update \\
	iReport		& 0		& 0 	& 0		& 0 & No update \\
	informa		& 31	& 0 	& 22	& 0 & No update \\
	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
	jFin		& 15	& 0		& 72	& 0 & No update \\
	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
	jasml		& 23	& 0		& 47	& 0 & No update \\
	jext		& 80	& 0		& 85	& 0 & No update \\
	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
	jmoney		& 0		& 0		& 0		& 0 & No update \\
	jparse		& 0		& 0		& 0		& 0 & No update \\
	\hline
	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
	%\hline
	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
	\hline
	Total		& 610	& 5		& 4231	& 52 	&\\
	\hline
\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
	\label{fig:sankey}
\end{figure}

@@

However, the -balanceSquareBrackets+ parameter only works on a small testing environment having toy programs or only small pairs from the full datasets. It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects. Please find the summary of all the testing scenarios in Table \ref{tab:summary}. %I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.

>>>>

\section*{Dataset}
In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{Qualitas}.

\section*{Stackoverflow-Qualitas Clones}
The results of 2 clone detectors: Simian and NiCad to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset are presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}

\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

\textbf{Qualitas-\textit{O}:} The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}. We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 664 \textit{ok-match} pairs that were investigated. The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.

@@

\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

@@

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
		\hline
		Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
		\hline
		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
		\hline
	\end{tabular} 
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
%	\label{tab:classification_new}
%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
%		\hline 
%		Classification & A & A' & B & C & D & E & F & Total \\ 
%		\hline
%		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
%		\hline
%		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
%		\hline
%		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
%		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
%		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
%		\hline
%	\end{tabular} 
%\end{table}

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{N}: Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & - & - & - & - & - & - & - & - \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & - & - & - & - & - & - & - & - \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & - & - & - & - & - & - & - & - \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ & - & - & - & - & - & - & - & - \\
		\hline
		Total & - & - & - & - & - & - & - & - \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification_new}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
		\hline
		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
		\hline
	\end{tabular} 
\end{table}

\subsection{Investigation of the unique clone pairs}

\textbf{Qualitas-\textit{O}:} In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.

@@

\textbf{Qualitas-N:}

\begin{table}[H]
	\centering
	\caption{Classification results of Simian$_{df}$ NiCad$_{df}$ individual unique pairs.}
	\label{tab:classification_indv}
	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{6mm}|R{8mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{8mm}|}
		\hline 
		\multirow{2}{*}{Classification} & \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ \cline{2-17}
		 & A & A' & B & C & D & E & F & Total & A & A' & B & C & D & E & F & Total \\ 
		\hline 
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 9,272 & & & & & & & & \\ \cline{2-8}
		\hline
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 6,831 & & & & & & & & \\ \cline{2-8}
		\hline
		TP/FP & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & 424 & & & & & & & &  \\

		\hline
		Unique SO fragments & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
		\hline
		Unique Q files & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
		\hline
		Unique Q files & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Projects that do not have resutls in Qualitas-\textit{N} but do have results in Qualitas-\textit{O}}
	\label{tab:tp_pairs}
	\begin{tabular}{l|r|r|r|r|p{5cm}}
	\hline
	\multirow{2}{*}{Project} & \multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{1}{c}{Qualitas-\textit{N}} \\ \cline{2-6}
			& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
	\hline
	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
	%\hline
	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
	Compiere	& 127	& 2		& 178	& 8 & No update \\
	axion		& 7		& 	0	& 12	& 0 & No update \\
	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
	colt		& 0		& 	0	& 5		& 0 & No update \\
	columba		& 14	&	0	& 177	& 0 & No update \\
	drawswf		& 0		&	0	& 0		& 0 & No update \\
	fit-java	& 0		& 0		& 2 	& 0 & No update \\
	freecs		& 5		& 0		& 22	& 0 & No update \\
	heritrix	& 16	& 0		& 190 	& 0 & No update \\
	iReport		& 0		& 0 	& 0		& 0 & No update \\
	informa		& 31	& 0 	& 22	& 0 & No update \\
	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
	jFin		& 15	& 0		& 72	& 0 & No update \\
	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
	jasml		& 23	& 0		& 47	& 0 & No update \\
	jext		& 80	& 0		& 85	& 0 & No update \\
	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
	jmoney		& 0		& 0		& 0		& 0 & No update \\
	jparse		& 0		& 0		& 0		& 0 & No update \\
	\hline
	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
	%\hline
	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
	\hline
	Total		& 610	& 5		& 4231	& 52 	&\\
	\hline
\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas files}
	\label{fig:sankey}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Sankey_proj}
	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
	\label{fig:sankey}
\end{figure}

@@

However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets. It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects. Please find the summary of all the testing scenarios in Table \ref{tab:summary}. %I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.
